Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-08-13 paper/revision/responseToReviewers.tex

\item \emph{There are several parameters that must be set in the experimentation. The reader may want to know if there is any specific parameter that is critical.}

$\rightarrow$ Considering the features design, we set the parameters to widely used values that have shown to be robust. We also ran a sensitivity analysis for the parameters that controls the proposed algorithm: scaling parameter $q$ and the number of clusters $M$. None of them are found to be critical providing that they are set in a reasonable range. It is worth noting that the scaling method is specifically designed for reducing sensitivity compared to the direct RBF kernel formulation.

\item \emph{What about M?}

$\rightarrow$ The number of clusters $M$ is indeed an important parameter. The higher $M$ is, the more complex the model and the computation are. Setting $M$ to 4 roughly states that there may be at most 4 different types of events in the given chunk of audio, here 30 sec. The analysis we added to the manuscript at the end of Section 7.

### 2018-08-13 paper/lostanlenRelevanceScattering.tex
updarte response to reviewer

The scaling parameter $q$ of the RBF kernels (see Eq.~\ref{eq:kc}) is set to $10\%$ of the number of data points to cluster.  As the number of Gaussians for the BoF approach, the numbers of clusters $M$ controls the level of abstraction. For each method, the parameter $M$ is set to $8$. It thus allows $8$ different types of observations to de modeled, which seems reasonable given the duration of the scene (30 seconds). Note that this is the only free parameter in the proposed method. However, except for $\emph{RbQ-a}$, the results are not very sensitive to the choice of $M$, as long as it is large enough to characterize the seen. For a numerical demonstration of this, please see the end of the next section.

@@

For a small number of clusters ($M = 1$ or $M = 2$), all methods perform worse, since not enough discriminative sound objects are extracted from the recording.
This corresponds a summary statistics model.
For $M = 4$, most methods perform well, since this allows for better characterization of various signal structures in the scenes.
As the number of clusters increases, the \emph{RbQ-a} method performs significantly worse for both scattering features and MFCCs since any distinct objects are averaged out by clusters representing the background.
The \emph{RbQ-w} and \emph{RbQ-c} methods do better in this regard, as they are better able to emphasize the clusters that discriminate well between scenes.

>>>>

The scaling parameter $q$ of the RBF kernels (see Eq.~\ref{eq:kc}) is set to $10\%$ of the number of data points to cluster.  As the number of Gaussians for the BoF approach, the numbers of clusters $M$ controls the level of abstraction. For each method, unless otherwise stated, the parameter $M$ is set to $8$. It thus allows $8$ different types of observations to be modeled, which seems reasonable given the duration of the scene (30 seconds). Note that this is the only free parameter in the proposed method. However, except for $\emph{RbQ-a}$, the results are not very sensitive to the choice of $M$, as long as it is large enough to characterize the seen. For a numerical demonstration of this, please see the end of the next section.

@@

For a small number of clusters ($M = 1$ or $M = 2$), all methods perform worse, since not enough discriminative sound objects are extracted from the recording. Please note that setting $M = 1$ is equivalent to the \emph{early} approach as this corresponds a summary statistics model.
For $M = 4$, most methods perform well, since this allows for better characterization of various signal structures in the scenes.
As the number of clusters increases, the \emph{RbQ-a} method performs worse for both scattering features and MFCCs since any distinct objects are averaged out by clusters representing the background.
The \emph{RbQ-w} and \emph{RbQ-c} methods do better in this regard, as they are better able to emphasize the clusters that discriminate well between scenes.
